intro

### 2022-05-24 06_Paper/ER-ED/TheoreticalBackground.Rmd
Update TheoreticalBackground.Rmd
Added a paragraph on why there is no objectively easiest strategy

In the original study by Westbrook et al.[-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies[@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.[-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al.[@Zerna2022]).

>>>>

In the original study by Westbrook et al.[-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide in an iterative procedure whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward, with the implicit assumption that the objectively easiest *n*-back level has the highest SV.
In the present study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies[@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
<!-- Kommentar Denise: ich pack jetzt erstmal das AO Paper zu der  Energie, die die Strategien brauchen, und andere Überlegungen hier her. bin mir aber nicht sicher, ob das woanders nicht besser passt.--> It could be assumed, that the antecedent-focused strategies, i.e. attentional deployment and cognitive change, require less effort, because according to Gross [-@Gross1998antecedent] these strategies apply when the emotional reaction has not fully developed, yet. 
In contrast, suppression would need ongoing effort, because it takes effect late in the emotion generating process and does not alter the emotion itself. 
A similar assumption has been made by Mesmer-Magnus et al. <!--Mesmer-Magnus, J. R., DeChurch, L. A., & Wax, A. (2012). Moving emotional labor beyond surface and deep acting: A discordance-congruence perspective. Organizational Psychology Review, 2(1), 6-53. https://doi.org/10.1177/2041386611417746 -->, who state that Surface Acting (the equivalent to expressive suppression in emotional labor research) is supposed to continuously require high levels of energy (hence effort). Deep Acting (which refers to reappraisal), in turn, only initially needs the use of energy. 
This would be in conflict with findings in our prevoius studies, that showed that many people choose expressive suppression because they evaluated it as less effortful, hence easy[@Scheffel2021].
Others define emotion regulation on a continuum from explicit, conscious, and effortful to implicit, unconscious, automatic and effortless <!--Gyurak, A., Gross, J. J., & Etkin, A. (2011). Explicit and implicit emotion regulation: a dual-process framework. Cogn Emot, 25(3), 400-412. https://doi.org/10.1080/02699931.2010.544160-->. This would mean, that all explicit strategies that have been proposed by the process model of emotion regulation are similarly effortful[@Gross1998antecedent].  <!--Schaut mal, ob ihr mit dieser Argumentation einverstanden seid-->
Similarly, the flexibility approach of emotion regulation also states, that there is no "best" strategy <!-- Gross, J. J. (2015). Emotion Regulation: Current Status and Future Prospects. Psychological Inquiry, 26(1), 1-26. https://doi.org/10.1080/1047840x.2014.940781-->. An emotion regulation attempt is adaptive, when the intended, individual goal is reached. Those attempts could also consist of sequences of regulatory efforts using different strategies, which might be effective and effortless only in this specific context.

Therefore, we have to add an additional step, which precedes the other steps and where the ER option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 €) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 €) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al.[-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see Figure \@ref(fig:ResponsePatterns)).
In a separate study, we will test our adapted paradigm together with a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al.[@Zerna2022]).
